---
title: "36-315 Interactive Graphis Project, Spring 2018"
author: "Devansh Kukreja (dkukreja), Oliver Liu (zhuoranl), Ross A Hemmel (rhemmel)"
date: "Due Wednesday, May 2, 2018 (11:59pm) on Canvas"
output: 
  html_document:
    toc:  true
    toc_float:  true
    code_folding:  show
runtime: shiny
---

#  Homework 11: Interaction

***
***

# Problem 0

**Administrative checklist**

* "We used Google's R style guide."

* "This submission is for the following group: Devansh Kukreja (dkukreja), Zhuoran Liu (zhuoranl), Ross A Hemmel (rhemmel)

***
***

The following problems are based on the first example from RStudio's [Interactive Documents](https://rmarkdown.rstudio.com/authoring_shiny.html) page. We will show a histogram and density plot for the Old Faithful dataset, and we will allow users to control the binwidth and bandwidth interactively.

Read the Old Faithful documentation file using `?faithful` to see what its variables and observations are.

As far as I can tell, the data were recorded in order across about 2 weeks. Just so that we can add a continuous variable to the dataset, let's assume that about half of the observations were taken during each week.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
df = read.csv("/Users/devanshkukreja/Box Sync/CMU 2018 Spring/Stat Vis - 36315/36315_interactive_graphics_project/dkukreja/adult_census_income.csv")

library(ggplot2)
library(tidyverse)
```

```{r}
# Clean and improve data
df <- mutate(df,
             education = factor(education,
                                levels=c("Preschool","1st-4th","5th-6th","7th-8th","9th","10th","11th","12th","HS-grad","Some-college","Assoc-voc","Assoc-acdm","Bachelors","Masters","Prof-school","Doctorate"),
                                ordered=TRUE))

```

# Problem 1: Shiny Outputs

*a. (0 points)  Run the existing app by clicking the "Run Document" button in RStudio. Play with the two inputs (dropdown and slider). Can you find a combination of histogram binwidth and density bandwidth adjustment for which the histogram and density plot look similar?*

*b. (20 points)  Modify the code below, so that the histogram and density plot are drawn using `ggplot2` instead of base R graphics. You only need to replace what's inside `renderPlot({...})`.*

* *Make a single call to `ggplot()`, specifying the `faithful` dataset. Map the `eruptions` variable to the x aesthetic, and map `..density..` to the y-aesthetic so the histogram and density plots will have the same scale.*
* *Add the two geoms. Use `input$n_breaks` and `input$bw_adjust` to specify the number of histogram bins and the density bandwidth adjustment.*
* *Make sure you have an appropriate title, axis labels, and data-source caption.*

```{r plot1, echo=FALSE, warning=FALSE, message=FALSE}
shinyApp(
  
  ui = fluidPage(
    inputPanel(
      radioButtons("metric", label='Metric:',
                   choices= c("Capital Gains", "Capital Losses")),
      
      checkboxInput("edges", label='Show Edge Entries (0 and 99999):')
    ),
    
    plotOutput("census_plot")
  ),
  
  server = function(input, output) {
    output$census_plot <- renderPlot({
      ## PUT YOUR GGPLOT CODE HERE ##
      df_cur = df
      if(!input$edges && input$metric == 'Capital Gains') df_cur <- filter(df, capital.gain < 99999 & capital.gain > 0)
      if(!input$edges && input$metric == 'Capital Losses') df_cur <- filter(df, capital.loss > 0)
      
      title = "Education Level and Investment Success"
      
      ggplot(df_cur, aes_string(x='education', y = ifelse(input$metric == 'Capital Gains', "capital.gain", "capital.loss"))) +
        geom_boxplot(alpha=0.7) +
        geom_point(alpha=0.3) +
        geom_jitter(width=0.1, height=0.1) +
        geom_smooth(aes(x=education.num)) +
        labs(title=title,
             x="Highest Education Level",
             y=input$metric)+
        theme(axis.text.x = element_text(angle = 45, hjust = 1))
    })
  },
  
  options = list(height = 550)
)
```

```{r plot2, echo=FALSE, warning=FALSE, message=FALSE}
shinyApp(
  
  ui = fluidPage(
    inputPanel(
      radioButtons("sex", label='Gender:',
                   choices = c("Both", "Male", "Female")),
      
      radioButtons("race", label='Race:',
                   choices = c("All","White", "Black", "Asian-Pac-Islander", "Amer-Indian-Eskimo", "Other"))
    ),
    
    plotOutput("census_plot")
  ),
  
  server = function(input, output) {
    output$census_plot <- renderPlot({
      ## PUT YOUR GGPLOT CODE HERE ##
      df_cur = df
      if(input$sex != 'Both') df_cur <- filter(df, sex == input$sex)
      if(input$race != 'All') df_cur <- filter(df_cur, race == input$race)
      
      title = sprintf("Education Level and Gender on Income (%d entries)", nrow(df_cur))
      
      ggplot(df_cur, aes_string(x='education', fill = 'income')) +
        geom_bar(position='fill') +
        theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
        labs(title = title,
             x="Highest Education Level",
             y="Proportion")
    })
  },
  
  options = list(height = 550)
)
```

***
***